### 2013-02-14 doc/xps2013/proposal.tex
some edits all over

\paragraph{Buffering requests to increase locality:} Grappa trades latency for throughput by aggregating network communication. The same idea could be applied to increase locality and amortize the cost of Flash accesses. Requests to nearby flash locations would be bucketed by flash page address for a limited time. When a sufficient number of requests have arrived for a page or when the requests time out, a single page request would be issued to the Flash layer; its result would be used to satisfy the individual requests.  The challenge with this approach is as storage size grows, the effectiveness of aggregation correspondingly decreases.  On the other hand, aggregation occurs for all global memory requests generated by any node in the system, so as aggregate system performance increases, aggregation performance actually \emph{increases} (up to the point that the network is saturated).

>>>>

% \paragraph{Buffering requests to increase locality:} Grappa trades latency for
% throughput by aggregating network communication. The same idea could be
% applied to increase locality and amortize the cost of Flash accesses. Requests
% to nearby flash locations would be bucketed by flash page address for a
% limited time. When a sufficient number of requests have arrived for a page or
% when the requests time out, a single page request would be issued to the Flash
% layer; its result would be used to satisfy the individual requests. The
% challenge with this approach is as storage size grows, the effectiveness of
% aggregation correspondingly decreases. On the other hand, aggregation occurs
% for all global memory requests generated by any node in the system, so as
% aggregate system performance increases, aggregation performance actually
% \emph{increases} (up to the point that the network is saturated).
